|

### 2023-04-08 paper.Rmd
fix unique lineups count

For clarity and consistency, the analysis in Sections \ref{power-analysis}-\ref{hetero-analysis}, uses only on results from lineups generated with uniform fitted values, a total of `r unique(pull(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"), unique_lineup_id))` lineups and `nrow(filter(vi_survey, !attention_check, !null_lineup))` evaluations. More evaluations were made using the uniform fitted value distribution, and it avoids potentially confounding results of the analysis by combining values from different power curves. We also expect that visual patterns are more clearly visible when the fitted value distribution is uniform. The results in Section \ref{effect-of-fitted-value-distributions} examine the effect of fitted value distribution on power.

>>>>

For clarity and consistency, the analysis in Sections \ref{power-analysis}-\ref{hetero-analysis}, uses only on results from lineups generated with uniform fitted values, a total of `r length(unique(pull(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"), unique_lineup_id)))` lineups and `nrow(filter(vi_survey, !attention_check, !null_lineup))` evaluations. More evaluations were made using the uniform fitted value distribution, and it avoids potentially confounding results of the analysis by combining values from different power curves. We also expect that visual patterns are more clearly visible when the fitted value distribution is uniform. The results in Section \ref{effect-of-fitted-value-distributions} examine the effect of fitted value distribution on power.
